### 2020-04-14 draft_ABP.tex
Updates from Overleaf

From the following equations for facets $\{F_{ij}\}$ of $A_n$
\[
F_{ac}+F_{bd}-F_{bc}-F_{ad}=\sum_{a\leq p<b\atop{c\leq q<d}}c_{pq}
\]
for $1\leq a<b<c<d\leq n+3$, ({\bf Zhenjie}: I conjecture that) we find the most economical way to get a degeneration which satisfies the above property is setting all $c$s on the RHS of 
\begin{align*}
    &F_{ac}+F_{bd}-F_{ad}=\sum_{a\leq p<b< q<d}c_{pq}\quad \text{for $a<b<c=b+1<d$ }\\
    \text{or}&\\
    &F_{1c}+F_{b,n+3}-F_{bc}=\sum_{1\leq p<b\atop{c\leq q<n+3}}c_{pq}\quad \text{for $a=1$ and $d=n+3$}
\end{align*}
to be zero, and all wanted degenerations can be got by setting $c$s in several above equations.

We can see what happens from mesh when we set $c$s to be zero in only one above equations: an equation above corresponds a big diamond whose top or bottom corner and all $c$s are zero. For example,
\begin{center}
	\begin{tikzpicture}
		\draw (-2,0) node[left] {$A$} -- (1,-3) node[below] {$0$}
		-- (3,-1) node[right] {$C$} -- (0,2) node[above] {$B$}-- cycle;
		\draw (-1,-1) -- (1,1);
		\draw (-1,1) -- (2,-2);
		\draw (0,-2) -- (2,0);
			\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,2) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (-1,1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,0) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,0) {};
	\end{tikzpicture}
\end{center}
this diamond tells us that
\[
A+C-B=0.
\]
Since $A,B,C\geq 0$, the above equation force $A$ and $C$ to vanish when $B=0$. Therefore, $B$ is no longer a facet of the degeneration. Similarly, it's pleasure to show that black points are all vanishing facets in the above example, and generally
the number of vanishing facets equals the number of deleted $c$s for degenerations of this type.

One can use these diamonds to build a degeneration with more vanishing facets. For example, in $A_3$
\begin{center}
\begin{tikzpicture}
	\fill[green!30] (2,1) -- (0,-1) -- (1,-2) -- (3,0);
	\fill[blue!30] (3,0) -- (2,-1) -- (3,-2) -- (4,-1);
	\draw[thick] (-2,-1) -- (1,2) -- (4,-1) -- (3,-2) -- (0,1);
	\draw[thick] (-1,-2) -- (2,1);
	\draw[thick] (-2,-1) -- (-1,-2);
	\draw[thick] (-1,0) -- (1,-2) -- (3,0);
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,0) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (3,0) {};
\end{tikzpicture}
\end{center}
after setting $c$s in green and purple diamonds to be zero, three facets (black points) vanish and building set after deletion is 
\[
\{\{0,1,2,3\},\{0,1,2\},\{0,1\},\{0\},\{1\},\{2\},\{3\}\}.
\]
One can further check that it's a cube or $A_1^3$.

(Conjecture: they are all binary.)

>>>>

From the following equations for facets $\{F_{ij}\}$ of $A_n$
\[
F_{ac}+F_{bd}-F_{bc}-F_{ad}=\sum_{a\leq p<b\atop{c\leq q<d}}c_{pq}
\]
for $1\leq a<b<c<d\leq n+3$, an economical way to get a degeneration which satisfies the above property is setting all $c$s on the RHS of 
\begin{align*}
    &F_{ac}+F_{bd}-F_{ad}=\sum_{a\leq p<b< q<d}c_{pq}\quad \text{for $a<b<c=b+1<d$ }\\
    \text{or}&\\
    &F_{1c}+F_{b,n+3}-F_{bc}=\sum_{1\leq p<b\atop{c\leq q<n+3}}c_{pq}\quad \text{for $a=1$ and $d=n+3$}
\end{align*}
to be zero, and all wanted degenerations can be got by setting $c$s in several above equations.

From the viewpoint of mesh, an equation above corresponds a big diamond whose top or bottom corner and all $c$s are zero. For example,
\begin{center}
	\begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]
		\draw (-2,0) node[left] {$A$} -- (1,-3) node[below] {$0$}
		-- (3,-1) node[right] {$C$} -- (0,2) node[above] {$B$}-- cycle;
		\draw (-1,-1) -- (1,1);
		\draw (-1,1) -- (2,-2);
		\draw (0,-2) -- (2,0);
			\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,2) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (-1,1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,0) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,0) {};
	\end{tikzpicture}
	\qquad \text{or}
	\qquad
	\begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]
		\draw (-2,0) node[left] {$A$} -- (1,-3) node[below] {$B$}
		-- (3,-1) node[right] {$C$} -- (0,2) node[above] {$0$}-- cycle;
		\draw (-1,-1) -- (1,1);
		\draw (-1,1) -- (2,-2);
		\draw (0,-2) -- (2,0);
			\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,0) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-3) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (-1,-1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,-2) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,-2) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-1) {};
	\end{tikzpicture}
\end{center}
we can see that
\[
A+C-B=0.
\]
Since $A,B,C\geq 0$, the above equation force $A$ and $C$ to vanish when $B=0$. Therefore, $B$ is no longer a facet of the degeneration. Similarly, black points are all vanishing facets in the above example, and generally
the number of vanishing facets equals the number of deleted $c$s for degenerations of this type.

One can use these diamonds to build a degeneration with more vanishing facets. For example, in $A_3$
\begin{center}
\begin{tikzpicture}
	\fill[green!30] (2,1) -- (0,-1) -- (1,-2) -- (3,0);
	\fill[blue!30] (3,0) -- (2,-1) -- (3,-2) -- (4,-1);
	\draw[thick] (-2,-1) -- (1,2) -- (4,-1) -- (3,-2) -- (0,1);
	\draw[thick] (-1,-2) -- (2,1);
	\draw[thick] (-2,-1) -- (-1,-2);
	\draw[thick] (-1,0) -- (1,-2) -- (3,0);
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,0) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (3,0) {};
	\node at (-2.5,-1) {$\{0\}$};
\node at (-0.5,-1) {$\{1\}$};
\node at (1.5,-1) {$\{2\}$};
\node at (3.5,-1) {$\{3\}$};
\node at (-1.6,0) {$\{0,1\}$};
\node at (0.4,0) {$\{1,2\}$};
\node at (2.4,0) {$\{2,3\}$};
\node at (-0.8,1) {$\{0,1,2\}$};
\node at (1.2,1) {$\{1,2,3\}$};
\node at (1,2.2) {$\{0,1,2,3\}$};
\end{tikzpicture}
\end{center}
after setting $c$s in green and purple diamonds to be zero, three facets (black points) vanish and building set after deletion is 
\[
\{\{0,1,2,3\},\{0,1,2\},\{1,2,3\},\{0,1\},\{2,3\},\{0\},\{3\}\}.
\]

Suppose $\mathscr D$ is the set of all vanishing facets in the building set, we can read from the mesh that
\[
F_{I'}=\sum_{I\not\in \mathscr D}M_{I'}^IF_I
\]
for any $I'\in \mathscr D$, where $M$ is a matrix with non-negative entries. Therefore,
\[
\prod_{I\in \mathscr A_n}u_{I}^{F_{I}}=
\prod_{I'\in \mathscr D}u_{I'}^{F_{I'}}
\cdot
\prod_{I\not\in \mathscr D}u_{I}^{F_{I}}=
\prod_{I\not\in \mathscr D}\biggl(
u_I\prod_{I'\in \mathscr D}u_{I'}^{M_{I'}^I}
\bigg)^{F_I},
\]
so the new $u$-variables of the degeneration are
\[
    \tilde u_{I}=u_I\prod_{I'\in \mathscr D}u_{I'}^{M_{I'}^I}
\]
for any $I\not\in \mathscr D$. 
%From the viewpoint of mesh, the product are taken over all diamonds whose $c$s are all zero, top (respectively, bottom) corner is a deleted element $I'$, bottom (respectively, top) corner is 0 and left or right corner is $I$, because for such diamond $F_{I'}=F_I+\cdots$ or $M^I_{I'}=1$.
For example, in the above example of $A_3$,
\[
F_{123}=F_{1}+F_2+F_3, \quad F_{12}=F_1+F_2, \quad F_{23}=F_2+F_3,
\]
so 
\begin{align*}
\tilde u_{1}&=u_1 u_{123} u_{12}=\frac{x_1x_{012}}{x_{12}x_{01}}\frac{x_{123}}{x_{0123}}\frac{x_{12}x_{0123}}{x_{123}x_{012}}=\frac{x_1}{x_{01}},\\
\tilde u_{2}&=u_2 u_{123} u_{12}u_{23}=\frac{x_2x_{123}}{x_{23}x_{12}}\frac{x_{123}}{x_{0123}}\frac{x_{12}x_{0123}}{x_{123}x_{012}}\frac{x_{23}}{x_{123}}=\frac{x_{2}}{x_{012}},\dots
\end{align*}

(Conjecture: they are all binary. In fact, I guess that $\tilde u_I\to 0$ is still given by $x_i\to 0$ for $i\in I$, then Chi's proof can be applied here.)
